Anonymous provision of services via blockchain

### 2022-03-08 access.tex
update analysis

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in a neutral position. One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

\item
  The customer can follow the protocol and move to a non-disadvantaged position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
\item
  The SP can do nothing and end up in a non-disadvantaged position \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
\end{itemize}

@@

\begin{itemize}
\item
  Following protocol:
  \begin{itemize}
  \item
    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in a neutral position, since he didn't spend his funds.
  \item
    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in a neutral position as he didn't receive the payment, nor spent his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

\item
  The customer can move the protocol forward to step 3, where if the
  SP follows the protocol then the customer can push the protocol forward
  up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\),
  otherwise if at any step the SP does not follow the protocol the
  customer can start a dispute which terminates the protocol at
  non-disadvantaged position, i.e.,
  \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\),
  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\),
  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\),
  \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\),
  \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \mathrm{n}} = -\), the customer hasn't received the
    result so he remains in a disadvantaged position.
  \item
    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract
    on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \mathrm{d}} = -\), the customer lose the case as the
    SP has still the opportunity to publish proof-of-provision within
    timeframe.
  \item
    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same
    reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position.
  \item
    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in a
    advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and ends up in a neutral position.
  \item
    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case
    and end up in a disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will
  ultimately put him in an advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
  the protocol, the customer can start a dispute and terminate in a
  non-disadvantaged position
  \(\sigma_{3, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can follow the protocol and move to a non-disadvantaged
  position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at a non-disadvantaged position
  \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \mathrm{n}} = -\), the customer hasn't received the result so he remains in disadvantaged position.
  \item
    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \mathrm{d}} = -\), the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe.
  \item
    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same
    reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in
    disadvantaged position.
  \item
    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in
    advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the
    case and end up in neutral position.
  \item
    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case
    and end up in a disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will
  ultimately put him in an advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
  the protocol, the customer can start a dispute and terminate in
  non-disadvantaged position
  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

\noindent \textbf
{Step 5. SP turn: Proof of provision}\label{step-5-publication-of-proof-of-provision}

@@

  \item
    \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
    result. Therefore, he remains in a disadvantaged position.
  \item
    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fulfilled the contract
    on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision.
  \item
    \(\sigma_{5, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in a disadvantaged position.
  \item
    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    an advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the
    case and end up in a neutral position.
  \item
    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in a disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol because it
  will ultimately put him in an advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), otherwise, in case of the SP not
  following the protocol, the customer can start a dispute and terminate
  in non-disadvantaged position
  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{5, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
    result but not the result yet.
  \item
    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision.
  \item
    \(\sigma_{6, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position.
  \item
    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment but didn't spend his
    resources.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the
    case and end up in a neutral position.
  \item
    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in a disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the position
  \(\sigma_{6, c, \mathrm{n}} = -\), which let's him move the protocol
  to a non-disadvantaged termination position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed
  the protocol start a dispute and win the case
  \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and end up in a non-disadvantaged position
  \(\sigma_{6, s, \mathrm{n}} = +\), or
  \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
    result. Therefore, he moves to an advantaged position.
  \item
    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision.
  \item
    \(\sigma_{7, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) the customer ends up in a disadvantaged position, as he ends up with incorrect result.
  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\) SP ends up in advantaged
    position as he received the payment but didn't spend his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the case and ends up in a neutral position.
  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP loses the case and ends up in a disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP hasn't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and ends up in a non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
\end{itemize}

@@

The diagram below shows the path of positions when the SP tries to misbehave and does not execute service after receiving the payment. The protocol ends up neutral to the customer and disadvantaged to the SP positions.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-misbehaviour-path.png}
\centering
\caption{Scenario of paths where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}

Ultimately, the rational path for both parties is to follow the protocol as shown in the diagram below.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-rational-path.png}
\centering
\caption{The scenario of path where both the customer and  the SP are behaving correctly}
\label{fig:well-behaviour}
\end{figure}

@@

With the fairness definition stated in the equation and the assumptions stated in Section \ref{assumptions}, our analysis indicates that the protocol achieves fairness.

>>>>

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position. One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

\item
  The customer can follow the protocol and move to the non-disadvantaged position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
\item
  The SP can do nothing and end up in the non-disadvantaged position \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
\end{itemize}

@@

\begin{itemize}
\item
  Following protocol:
  \begin{itemize}
  \item
    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in the neutral position as he did not spend his funds.
  \item
    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

\item
  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\), \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and end up in the non-disadvantaged position \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\), \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \mathrm{n}} = -\), the customer has not received the result, so he remains in the disadvantaged position. 
  \item
    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \mathrm{d}} = -\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
  \item
    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position.
  \item
    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment. 
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and ends up in the neutral position.
  \item
    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\sigma_{3, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \mathrm{n}} = -\), the customer has not received the result, so he remains in the disadvantaged position. 
  \item
    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
  \item
    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position. 
  \item
    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment. 
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in a neutral position. 
  \item
    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
\end{itemize}

\noindent \textbf
{Step 5. SP turn: proof of provision}\label{step-5-publication-of-proof-of-provision}

@@

  \item
    \(\sigma_{5, c, \mathrm{n}} = -\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
  \item
    \(\sigma_{5, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
  \item
    \(\sigma_{5, s, \mathrm{d}} = +\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position.
  \item
    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position. 
  \item
    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\sigma_{7, c, \mathrm{n}} = +\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{5, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \mathrm{n}} = -\), the customer gets a hash of the result but not the result yet.
  \item
    \(\sigma_{6, s, \mathrm{n}} = +\), the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
  \item
    \(\sigma_{6, s, \mathrm{d}} = +\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position.
  \item
    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position.
  \item
    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the position \(\sigma_{6, c, \mathrm{n}} = -\), which lets him move the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP has not followed the protocol start a dispute and win the case \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and end up in a non-disadvantaged position \(\sigma_{6, s, \mathrm{n}} = +\), or \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \mathrm{n}} = +\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
  \item
    \(\sigma_{7, s, \mathrm{n}} = +\), the SP position has not changed. 
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
  \item
    \(\sigma_{7, s, \mathrm{d}} = +\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position.
  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP has not followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and ends up in the non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
\end{itemize}

@@

The figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment. The customer reacts by starting a dispute, and the protocol ends up neutral to the customer and disadvantaged to the SP positions.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-misbehaviour-path.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}

Ultimately, the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational} below.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-rational-path.png}
\centering
\caption{Transitions of positions where where both the customer and the SP are behaving correctly}
\label{fig:rational}
\end{figure}

@@

Using the fariness definition~\ref{fairness} and the assumptions stated in section~\ref{assumptions}, our analysis indicates that the protocol achieves fairness.
